---
author: "Tom Palmer"
title: "An example Metropolis Beamer presentation using R Markdown compiled in the rmdmetro Docker container"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  beamer_presentation:
    slide_level: 2
    theme: metropolis
    latex_engine: xelatex
    citation_package: biblatex
    incremental: no
fontsize: 11pt
classoption:
 - compress
 - "aspectratio=169"
header-includes:
 \hypersetup{colorlinks, filecolor=red, citecolor=black, linkcolor=brown, urlcolor=blue}
 \setbeamertemplate{frametitle continuation}{}
 \usepackage{appendixnumberbeamer}
 \usepackage[authordate, backend=biber, url=false, isbn=false, eprint=false, doi=false, uniquename=false, giveninits=true, maxcitenames=2]{biblatex-chicago}
 \renewcommand*{\bibfont}{\scriptsize}
 \DeclareMathOperator{\E}{\mathbb{E}}
 \setmainfont{Fira Sans Book}
 \setsansfont[BoldFont={Fira Sans SemiBold}]{Fira Sans Book}
 \setmathfont{Fira Math} 
 \setmonofont[Contextuals={Alternate}]{Fira Code}
 \renewcommand\UrlFont{\sffamily}
 \newcommand{\ind}{\perp \!\!\! \perp}
 \metroset{sectionpage=none}
 \makeatletter
 \beamer@ignorenonframefalse
 \makeatother
bibliography: bibliography.bib
biblio-title: References
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
                      out.extra = "keepaspectratio",
                      echo = FALSE)
options(digits = 3)
```

## Outline{.allowframebreaks .t}

\tableofcontents

# Part 1

## Introduction{.allowframebreaks .t}

- This is a test
  - of the Docker container

## A slide with a citation{.allowframebreaks .t}

* @greenland-2011 define collapsibility as
\vspace{.3cm}

> When an adjustment does not alter a measure, the measure is said to be collapsible over *C* or invariant with respect to the adjustment. Conversely, if an adjustment alters a measure, the measure is said to be non-collapsible over *C*.

## A slide with some maths{.allowframebreaks .t}

- @neuhaus-1993 explained that where $f(p)$ is the link function
  - GLMs: $f(\E[Y]) = \eta$
  - e.g. logit link; $\log\left(\frac{p}{1-p}\right) = \eta$
- $\nu$ is the conditional association between $X$ and $Y$ (on the scale of the linear predictor)
- Characteristic collapsibility function (CCF) $g_{\nu}(p)$, named by @daniel-2020, maps $P(Y|X=0,C)$ to $P(Y|X=1,C)$ (e.g. part (b) of first figure)

$$
\text{CCF:}\ g_\nu(p) = f^{-1}\left\{ f(p) + \nu \right\}
$$

- Take away: **A parameter is said to be non-collapsible when its CCF is non-linear**

# Part 2

## A slide with some code and output{.allowframebreaks .t}

```{r}
set.seed(8910)
x <- c(0, 0, 1, 1, 0, 0, 1, 1)
y <- c(0, 1, 0, 1, 0, 1, 0, 1)
c <- c(0, 0, 0, 0, 1, 1, 1, 1)
r <- c(20, 5, 15, 10, 10, 15, 5, 20)
dat <- data.frame(x, y, c, r)
datlong <- reshape::untable(dat[, 1:3], num = dat$r)
```

* Estimate the marginal odds ratio
```{r echo=TRUE}
fitor <- glm(y ~ x, data = datlong, family = binomial)
```

* A nice kable table
```{r}
knitr::kable(exp(cbind(coef(fitor), confint.default(fitor))))
```

## A slide with a plot{.allowframebreaks .t}
```{r, out.height="75%"}
plot(1:10)
```
